Bias correction in GLMs

### 2021-08-25 bias_correction.rmd
Population averaging seems to work!

## Pop. average
### Quantiles
reff_vareff_age_quant_multi <- varpred(reff_mod_multi, "age", isolate=TRUE, pop.ave="quantile", modelname="quantiles")
### Population
reff_vareff_age_pop_multi <- varpred(reff_mod_multi, "age", isolate=TRUE, pop.ave="population", modelname="Population")
binned_df <- binfun(reff_mod_multi, focal = "age", non.focal = c("expenditure", "wealthindex"), bins=50)

@@

## Pop. average
### Quantiles
reff_vareff_expenditure_quant_multi <- varpred(reff_mod_multi, "expenditure", isolate=TRUE, pop.ave="quantile", modelname="quantiles")
### Population
reff_vareff_expenditure_pop_multi <- varpred(reff_mod_multi, "expenditure", isolate=TRUE, pop.ave="population", modelname="Population")
binned_df <- binfun(reff_mod_multi, focal = "expenditure", non.focal = c("age", "wealthindex"), bins=50)

>>>>

## Pop. average
### Quantiles
reff_vareff_age_quant_multi <- varpred(reff_mod_multi, "age", isolate=TRUE, include.re=TRUE, pop.ave="quantile", modelname="quantiles")
### Population
reff_vareff_age_pop_multi <- varpred(reff_mod_multi, "age", isolate=TRUE, include.re=TRUE, pop.ave="population", modelname="Population")
binned_df <- binfun(reff_mod_multi, focal = "age", non.focal = c("expenditure", "wealthindex"), bins=50)

@@

## Pop. average
### Quantiles
reff_vareff_expenditure_quant_multi <- varpred(reff_mod_multi, "expenditure", isolate=TRUE, pop.ave="quantile", include.re=TRUE, modelname="quantiles")
### Population
reff_vareff_expenditure_pop_multi <- varpred(reff_mod_multi, "expenditure", isolate=TRUE, pop.ave="population", include.re=TRUE, modelname="Population")
binned_df <- binfun(reff_mod_multi, focal = "expenditure", non.focal = c("age", "wealthindex"), bins=50)
